---
title       : Avia incidents investigation time
subtitle    : Slides for Coursera "Developing Data Products" peer review
author      : Alexander Minyushkin
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Introduction

After crash of Malaysia Airlines Flight MH17 on 2014 July 17, there were many complaints that investiagtion takes too long time.

So I decide to take a look at statistics and get some understanding of reasonable time for aviation incidents investigations.

--- .class #id 

## Data 

Using Google search I found some relevant open data here http://catalog.data.gov/dataset/ntsb-aviation-accident-database-extract-of-aviation-accident-records-since-1982--ntsb-1962

XML file is pretty big, so here you can see how it looks like in general:
```{r cache=FALSE}
skipout<-lapply(readLines("AviationData_sample.xml"), function(x) cat(paste0(x, "\n")))

```


--- .class #id 

## Parsing Data 

Reading data using XML package

```{r cache=FALSE}
library(XML)
options(stringsAsFactors = FALSE)

d <- xmlParse("AviationData_sample.xml")

els <- getNodeSet(d, "//x:ROW", "x")
attrs <- sapply(els, function(x) xmlAttrs(x)) 

out <- data.frame(t(attrs))

```



--- .class #id 


## Parsing Data Continues

After brief review I found that dates in the file stored in different formats, so I make a function to correct this.

```{r}
converMixedDate <- function(x){
  y <- strptime(x, tz = "", "%m/%d/%Y" )  
  y[is.na(y)] <- strptime(x[is.na(y)], tz = "", "%Y-%m-%d" )      
  y
  
}

converMixedDate(out$EventDate)

```

Ignore timezone for now, it is not used later

--- .class #id 

## Data Cleanup

When I found that there are still few dates was not processed properly I decided ti exclude them from data frame

```{r eval = F}

# Still have a mess in dates. Just clean them up for now
out <- out[ !is.na(out$P_Date) & !is.na(out$E_Date),]

out$investigationTimeDays <- as.numeric(out$P_Date - out$E_Date) / 24/3600

# cleanup some more inconsystencies
out <- out[out$investigationTimeDays>0,]


```

--- .class #id 

## Results

Now I can look at plots like this

http://alexander.shinyapps.io/avia_project


--- .class #id 
